### 2020-01-10 report/02-methods.Rmd
Peripherical species testing

```{r}
myload(community_analysis, dir = data_common)

com <- community_analysis %>%
  dplyr::select(opcod, species, biomass) %>%
  dplyr::left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  dplyr::filter(!is.na(station)) %>%
  dplyr::group_by(station) %>%
  tidyr::nest() %>%
  mutate(data = map(data, function (.data) {
      .data %<>%
	tidyr::spread(species, biomass) %>%
	dplyr::select(-opcod) %>%
	dplyr::mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
	dplyr::summarise_all(list(~ sum(. != 0) / n()))
      return(.data)
      }
    )
  )
occurence_sp_st <- com %>%
  unnest() 
%>%
  dplyr::mutate_if(is.double, list(~ ifelse(is.na(.), 0, .)))

@@

```{r}
sp_per <- med_occ[med_occ$med_occ < .30,]$sp

@@

>>>>

```{r sp-occ}
myload(community_analysis, dir = data_common)

com <- community_analysis %>%
  dplyr::select(opcod, species, biomass) %>%
  dplyr::left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  dplyr::filter(!is.na(station)) %>%
  dplyr::group_by(station) %>%
  tidyr::nest() %>%
  mutate(data = map(data, function (.data) {
      .data %<>%
	tidyr::spread(species, biomass) %>%
	dplyr::select(-opcod) %>%
	dplyr::mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
	dplyr::summarise_all(list(~ sum(. != 0) / n()))
      return(.data)
      }
    )
  )
occurence_sp_st <- com %>%
  unnest()

@@

###### Species peripherical globally

```{r stab-sp-occ, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}
sp_per <- med_occ[med_occ$med_occ < .30,]$sp

@@

```{r}
test %>%
  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
  ggplot(aes(x = log10(richness_med), y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type), rows = vars(stab))

###### Species peripherical by station

```{r}

threshold_occ <- c(0, .10, .30, .60, .90)

res_sync_occ_st <- map_dfr(threshold_occ, function (.threshold) {

  # List of sp to rm
  sp_to_rm <- occurence_sp_st %>%
    gather(sp, occ, -station) %>%
    group_by(station) %>%
    filter(occ < .threshold) %>%
    summarise(sp2 = list(unique(sp)))

  # Rm species by station
  truncated_com <- community_analysis %>%
    left_join(select(op_analysis, opcod, station), by = "opcod") %>%
    filter(!is.na(station)) %>%
    group_by(station) %>%
    nest() %>%
    left_join(sp_to_rm, by = "station") %>%
    mutate(
      output = map2(data, sp2, function (.data, sp_vec) {
	rm_sp_from_com(com = .data, sp_to_rm = sp_vec)
  })
      ) %>%
  unnest(output) %>%
  select(-station)

  sync <- compute_com_synchrony(
    .op = op_analysis,
    com = truncated_com)

  sync$type <- .threshold 
  sync$biomass_stab <- 1 / sync$cv_com

  return(sync)
    })

res_sync_occ_st %>%
  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
  ggplot(aes(x = richness_med, y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type), rows = vars(stab))
```

Removing the peripherical species nor at the global scale neither at the station
scale do not affect the stability-diversity relationship.
